---
title: "document_creation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# references: 

example:
https://cran.r-project.org/web/packages/golem/vignettes/a_start.html

example applied:
https://towardsdatascience.com/production-grade-r-shiny-with-golem-prototyping-51b03f37c2a9

communication between modules: 
https://shiny.rstudio.com/articles/communicate-bet-modules.html

testing: 
https://shiny.rstudio.com/articles/integration-testing.html

# objective: 

define a path as links, like graph nodego links. 
ex: from: step_a ; to: step_b

define events that happen in each node. remember an event is a label that happens at a time and might have a value. 
ex: event: step_a date|datetime: 2021-01-01 value: 10

visualize path of nodes, how they are connected and some statistic on each node,
ex: event: step_a|n:22; event:step_b; n:20

# define ui: 

data load: a place where you can load the data. excel for now as its how data is arriving :/
- links data: an excel with specific sheet name to load. with format from|to
- event data: an excel with specific sheet name to load. with format event|datetime|value

data explore: a place where you can see what data has been loaded
- data preview: 
-- data table with loaded links data
-- data table with loaded event data

visualization: 
- network visualization with specific filters

# process of this app creation

## generic:

- create: rstudio > new project > shiny with golem > select cran valid name ( camel case NOT snake case)
- repo: create a github, 
- fill: dev/01_start.R # some config
- execute: golem::set_golem_options() # options :p
- execute: golem::use_recommended_tests() # initialize test structure
- execute: golem::use_recommended_deps() # initialize dependencies
- execute: golem::use_utils_ui() # ui utilities
- execute: golem::use_utils_server() #server utilities
- execute: usethis::use_package("shinipsum") # for mocking parts.
- execute: usethis::use_package("shinydashboard") # ui: custom presentation
- execute: usethis::use_package("shinydashboardPlus") # ui: custom presentation

- execute: golem::add_fct( "helpers" ) # for business functions
- execute: golem::add_utils( "helpers" ) # for utility functions ( utility = more abstract than business)

- execute: golem::add_js_file("script") # just to have a js file script
- execute: golem::add_js_handler("script")  # just to have a js handler script
- execute: golem::add_css_file("custom") # just to have custom css
- execute: usethis::use_data_raw() # for having some data; and define package data estructure

- create /inst/extdata: for loading the external demo data.
- execute: usethis::use_package("readxl") # to use sample data in case 1

## custom: 

- execute: golem::add_module(name = 'data_load') # structure: modules
- execute: golem::add_module(name = 'data_explore') # structure: modules
- execute: golem::add_module(name = 'data_viz') # structure: modules

- edit app_ui.r

# validate it works. 

devtools::install()
pathEventDataExplorer::run_app()


# continue development


# issues:

- the mod divided app doesnt work well. 
-- for testing: https://shiny.rstudio.com/articles/integration-testing.html
--- still under development so it doesnt count.
-- main issue: uploading seems ok , but id does not print the paths of reactive upload.
--- also as it doesnt load, i cant explore that on other modules.


## mod upload problem

cannot make that other module reads data read in module upload
as it was holding everything, i moved the uploads from the module to the main component

## for magritrr intertragion: 
usethis::use_pipe() # for adding the stuff
devtools::document() # for refreshing
desc::desc_get_deps("DESCRIPTION") # to see if apears

## visnetwork inside a module

FIXME: 
may be because of namespaces and custom JS , the names  or ids are not ok.
input_network_click_node
look at this on mod_data_viz 

## restarting interrupted promise evaluation

somewhere when loading data

## filtering dates have issues too. 

changed when using complete sample file

got to review when events sheet is not completed.

# validate external data is created

```{r}
sample_data_links_events_path <- system.file("extdata", "sample_data_links_events.xlsx", package = "pathEventDataExplorer")
sample_data_links <- readxl::read_xlsx(sample_data_links_events_path,sheet = "links")
sample_data_links <- readxl::read_xlsx(sample_data_links_events_path,sheet = "events")

```

